\lightkurve: a Python package for Kepler \& TESS time series data analysis

### 2018-02-21 paper/ms.tex
update paper
Geert ruined the contents

\newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}}
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}

@@

\title{An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}}

@@

\section{Introduction} \label{sec:intro}
NASA's Kepler and \KTWO~missions have been delivering high-precision time
series data for a wide range of stellar types.

>>>>

\newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
\newcommand{\tess}{TESS}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}}
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}

@@

\title{\lightkurve: a Python package for Kepler \& TESS time series data analysis}

@@

\section{Introduction} \label{sec:intro}
NASA's Kepler, \KTWO, and \tess~missions have been delivering high-precision time
series data for a wide range of stellar types.
Cite Borucki et al for Kepler, Howell et al for K2, XXX for TESS.

While these missions have powerful pipelines which deliver high-precision
lightcurves for many objects (citation), analyses tailored for specific
science cases can often optimize the analysis.
For example:
1) a bigger aperture mask has been shown to yield additional planets in Kepler-XXX (cite Isabel),
2) custom tailored PSF photometry has been shown to disentangle the signals of stars in
dense clusters (cite Libralato et al),
3) the official pipelines tend to be optimized for signals at the duration of typical
planet transits (6 hours) and are not optimized for long-term trends such as those
seen in AGN (cite Krista Lynn Smith).

Explain PyKE exists and how it differs.
In this paper, we present a new Python package which makes the custom analysis
of target easy.  Based on AstroPy (cite Astropy).

Explain the structure of the paper and announce that we will show examples
of the 3 key features: manipulating lightcurves, creating lightcurves,
and removing systematics from lightcurves.

\section{Package overview}

Maybe include a class diagram here, or a table of the modules or classes.

Maybe include a table or graph listing the key functions of the key classes,
e.g.
Lightcurve: cdpp, fold, stitch, plot
TargetPixelFile: tolightcurve, plot

\section{Examples of key features}

\subsection{Working with lightcurves}

flatten, fold, finding planets, from archive...

\subsection{Making your own lightcurves from target pixel files}

explain TPFs, aperture photometry, and PSF photometry

\subsection{Removing systematics from lightcurves}

We only intend to provide simple tools.
Ideally, systematics are removed simultaneously with fitting a model (e.g. Montet and DFM 2015).

\section{Future work}

Explain PSF photometry needs users and data-driven model capability.

We do not intend to implement transit fitting, more advanced detrending, etc.
Instead, lightkurve intends to provide the building blocks needed to build
or interact with such packages.

We intend to add many tutorials.

Explain how people can contribute.

\section{Conclusions}

we will discuss => we have discussed
